---
title: "data_cleaning_for_noobs"
author: "group 1"
date: "11/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Cleaning

TO DO :
- NA en char dans certaines colonnes, à reformatter
- Régler pb des latitudes / longitudes manquantes
- Rendre avertissements silencieux


#### Libraries import
```{r}
library(tidyverse)
library(magrittr)
library(readr)
library(stringr)
library(lubridate)
library(purrr)

Sys.setlocale(locale="en_US.UTF-8")

rm(list = ls())
```

#### Read data and primary data cleaning

Read the data:

```{r}
mapping_villes <- data.frame(read_delim("datasets/mapping_villes.csv", delim = ";"))

all_files <- c("datasets/arnaud_scrapping.csv", 
               "datasets/scrapped_listings_1_1_500.csv",
               "datasets/scrapped_listings_1_501_750.csv",
               "datasets/scrapped_listings_1_751_1000.csv",
               "datasets/scrapped_listings_1_1000_1500.csv",
               "datasets/scrapped_listings_1_1501_2000.csv",
               "datasets/scrapped_listings_1_2001_2400.csv",
               "datasets/scrapped_listings_1_2401_3000.csv",
               "datasets/scrapped_listings_1_3001_4000.csv",
               "datasets/scrapped_listings_1_4001_4500.csv",
               "datasets/scrapped_listings_1_4501_5500.csv",
               "datasets/scrapped_listings_1_6501_7500.csv",
               "datasets/scrapped_listings_1_7501_8500.csv",
               "datasets/scrapped_listings_2_1_250.csv",
               "datasets/scrapped_listings_2_251_500.csv",
               "datasets/scrapped_listings_2_501_750.csv",
               "datasets/scrapped_listings_2_751_1000.csv",
               "datasets/scrapped_listings_3_1_250.csv",
               "datasets/scrapped_listings_3_251_500.csv",
               "datasets/scrapped_listings_3_501_750.csv",
               "datasets/scrapped_listings_3_751_1000.csv")

# Read all

all_df <- map(all_files, ~read_csv(.x))

# For one dataset, we have a different ordering of the columns ¯\_(ツ)_/¯

names(all_df[[1]]) <- c("X1","url","is_listing_deleted", "brand", "modele","address_particulier","address_pro","name_pro","Année","Autres informations","Carrosserie","Emissions de CO2", "Energie","Kilométrage", "Nb de portes", "Nombre de places", "Prix", "Puissance fiscale", "Puissance réelle", "Transmission", "V1", "Garantie mécanique", "Consommation mixte", "Contrôle technique", "Couleur intérieur", "Type de peinture carrosserie",  "Etat du véhicule", "Option equipement Sécurité", "Option/Equipement Confort intérieur", "Option/equipement extérieurs", "Marque")

# Row bind into data

data <- map_df(all_df, ~bind_rows(.x))
```

Remove the deleted listings, and the useless column that is X1, and V1:

```{r}

data <- data %>% 
  filter(is_listing_deleted == 0 
         & !(is.na(Prix))
         & !(is.na(Carrosserie))) %>% 
  dplyr::select(-X1, -is_listing_deleted, -V1)


data %>% dim()

data <- data.frame(data)
data <- data %>% head(3000)


```

#### Get Postal Code Function

For now, we will focus on retrieving the postal code from the address and the city from mapping_villes.csv (source : http://www.nosdonnees.fr/wiki/index.php/Fichier:EUCircos_Regions_departements_circonscriptions_communes_gps.csv.gz)

We'll use a regular expression to find the postal code : "(([0-8][0-9])|(9[0-5])|(2[ab]))[0-9]{3}"


```{r}
get_postal_code <- function(address) {
  # Get all the strings that match a possible postal code
  poss_postal_codes <- str_match_all(address, "(([0-8][0-9])|(9[0-5])|(2[ab]))[0-9]{3}")[[1]][,1]
  l <- length(poss_postal_codes)
  # If there isn't any, return NA
  if (l == 0) {
    NA
  }
  # If there is just one, good, we keep that one
  else if (l == 1) {
     poss_postal_codes[1]
  } 
  # If there are many, we test them again, considering that scenario : we have both a postal box (BP) and a postal code. We want the one that is most likely to be a postal code (should usually end with a 0), and keep that one.
  # Note: we don't use that for everything because some postal codes end don't end with 0, ex in Paris : 75001.
  else {
    better_postal_code <- str_match(poss_postal_codes, "(([0-8][0-9])|(9[0-5])|(2[ab]))[0-9]{2}[0]")[,1]
    better_postal_code[!is.na(better_postal_code)]
    }
}
```

#### Get City Function

```{r}
#1. Pour les particuliers : 
  
get_city_particulier <- function(address){
  
  spl <- str_split(str_trim(address)," ")
  b <- str_locate(address, str_c("(",str_match(spl,"(([0-8][0-9])|(9[0-5])|(2[ab]))[0-9]{3}")[[1]],")"))[1]
  a <- str_locate(address, str_match(spl,"-"))[2]
  
  city <- str_sub(address, a + 2, b - 3) # Pour l'instant on a récupéré ce qu'il y a entre le premier tiret et le code postal
  
  if (is.na(city)) {
    return(NA)
    } 
  else {
    city <- str_remove_all(city, "[0-9]+")
    city <- str_trim(city, side = "both")
    if (is.na(str_match(city,"- ")))
      {
      return(city)
      } else {
        city <- str_sub(city, str_locate(city,"- ")[2] + 1)
        return(city)
    } # Là on règle le problème des prénoms composés dans la colonne addresse 
    } # Là on règle le problème de type "Paris 14" qui devient "Paris"
}

#2. Pour les pros :

get_city_pro <- function(address, pc){
  if (!is.character(pc)) {
    return(NA)
  } else {
  spl <- str_trim(address)
  pcmatch <- str_match(spl, pc)
  if (is_empty(pcmatch)) {
    return(NA)
  } else {
  b <- str_locate(address, pcmatch[[1]])[2]
  city <- str_trim(str_remove_all(str_sub(address, b+2), "[0-9]+"))
  return(city)
  }
  }
}
```

#### Remove Accents Function

```{r}
#Fonction pour retirer les accents
unaccent <- function(text) {
  text <- gsub("['`^~\"]", " ", text)
  text <- iconv(text, to="ASCII//TRANSLIT//IGNORE")
  text <- gsub("['`^~\"]", "", text)
  return(text)
}
```

#### Create Postal_Code_City Function

```{r}
create_postal_code_city <- function(pc, city) {
  as.character(
    unaccent(
      gsub(
        "saint", 
        "st", 
        tolower(
          str_remove_all(
                    str_c(pc,city),
                          "[- ]+"
                    )
          )
        )
      )
  )
}
```

#### Get Age Function

```{r}
french_months <- c(
                   "janvier", 
                   "février", 
                   "mars", 
                   "avril",
                   "mai",
                   "juin",
                   "juillet",
                   "août",
                   "septembre",
                   "octobre",
                   "novembre",
                   "décembre"
                   )

clean_month_year <- function(my) {
  my = str_remove(my, "\nAssurance auto : Comparez")
  my_split <- str_split(my, " ")[[1]]
  if (all(is.na(my_split))) {
    NA
  }
  else if (length(my_split) == 1) {
    #ymd(str_c(y_split_test, "-01-01"))
    ymd(str_c(my_split, "-01-01"))
  }
  else if (length(my_split) == 2) {
    ymd(
      str_c(
        my_split[2],
        "-",
        str_pad(
          string = as.character(
            which(
              french_months %in% str_to_lower(my_split)[1]
              )
            ), width = 2, pad = "0"),
        "-01"
        )
      )
  }
  else { NA }
}

ymd("1970-10-23")
```


#### Mapping Villes Cleaning

```{r}
names(mapping_villes) <- c("eu_circo","code_region", "nom_region", "chef_lieu_region", "numero_departement","nom_departement","prefecture","numero_circonsription","nom_commune","codes_postaux","code_insee","latitude", "longitude","eloignement")

relevant_mapping_villes <- mapping_villes %>% 
  dplyr::select(code_region, nom_region, numero_departement, nom_departement, nom_commune, codes_postaux, latitude, longitude) %>% 
  mutate(codes_postaux_commune = map2_chr(codes_postaux, nom_commune, create_postal_code_city))
```

#### Final Columns Cleaning

```{r}
# PB WARNINGS? SUPPRESS WARNINGS NE MARCHE PAS. POTENTIELLEMENT ON PEUT SE PASSER DE MAP SI ON ENLEVE LES FOR?

new_data <- 
data %>% 
  # Modele cleaning - some modeles have had a problem with the scraping, they have "euro" in it
  filter(is.na(str_match(data$modele,"euro"))) %>% 
  mutate(
         brand = str_remove(brand, " occasion")[1],
         name_pro = str_trim(name_pro),
         all_address = coalesce(address_particulier, address_pro),
         postal_codes = map(all_address, get_postal_code),
         city_particulier = map(address_particulier, get_city_particulier),
         city_pro = map2(address_pro, postal_codes, ~get_city_pro(.x, .y)),
         all_city = coalesce(city_particulier, city_pro),
         postal_code_city = map2(postal_codes, all_city, create_postal_code_city) ,
         is_pro = map(name_pro, function(x) 1 - is.na(x)),
         date = map(Année, clean_month_year),
         pneus_hiver = str_detect(Autres.informations, "Pneus hiver")*1,
         barres_de_toit = str_detect(Autres.informations, "Barres de toit")*1,
         premiere_main = str_detect(Autres.informations, "Première main")*1,
         non_fumeur = str_detect(Autres.informations, "Véhicule non fumeur")*1,
         stationne_dans_garage = str_detect(Autres.informations, "Stationne dans un garage")*1,
         sous_garantie_constructeur = str_detect(Autres.informations, "Sous garantie constructeur")*1,
         attelage = str_detect(Autres.informations, "Attelage")*1,
         sous_garantie_autre_que_constructeur = str_detect(Autres.informations, "(autre que constructeur)")*1,
         cons_mixte_l_by_100km = str_remove(Consommation.mixte, "\nlitres / 100 km"),
         emissions_co2_g_by_km = str_remove(Emissions.de.CO2, "\ng/km"),
         kilometrage_km = str_remove(str_remove(Kilométrage, "\nkm")," "),
         nb_portes = str_remove(str_remove(Nb.de.portes, " avec hayon"),c(" portes")),
         hayon = str_detect(Nb.de.portes, "hayon")*1,
         nb_places = str_remove(Nombre.de.places, "\nplaces"),
         prix_euros = str_remove(str_remove(Prix, " €"), " "),
         puissance_fiscale_cv = str_remove(Puissance.fiscale, "\nCV"),
         puissance_reelle_ch = str_remove(Puissance.réelle, "\nCh"),
         garantie_mecanique_mois = str_remove(Garantie.mécanique, " mois"),
         abs = str_detect(Option.equipement.Sécurité, "ABS")*1,
         esp = str_detect(Option.equipement.Sécurité, "ESP")*1,
         regulateur_vitesse = str_detect(Option.equipement.Sécurité, "Régulateur de vitesse")*1,
         asr = str_detect(Option.equipement.Sécurité, "ASR")*1,
         alarme_antivol = str_detect(Option.equipement.Sécurité, "Alarme antivol")*1,
         direction_assistee = str_detect(Option.Equipement.Confort.intérieur, "Direction assistée")*1,
         banquette_ar = str_detect(Option.Equipement.Confort.intérieur, "Banquette AR 1/3 - 2/3")*1,
         radio_cd = str_detect(Option.Equipement.Confort.intérieur, "Radio/CD")*1,
         fermeture_centralisee = str_detect(Option.Equipement.Confort.intérieur, "Fermeture centralisée")*1,
         vitres_electriques = str_detect(Option.Equipement.Confort.intérieur, "Vitres électriques")*1,
         allumage_auto_feux = str_detect(Option.equipement.extérieurs, "Allumage automatique des feux")*1,
         peinture_metallisee = str_detect(Option.equipement.extérieurs, "Peinture métallisée")*1,
         retroviseurs_electriques = str_detect(Option.equipement.extérieurs, "Rétroviseurs électriques")*1,
         roues_alliage_léger = str_detect(Option.equipement.extérieurs, "Roues alliage léger")*1,
         fap = str_detect(Option.equipement.extérieurs, "FAP")*1
         ) %>% 
  mutate_if(is.list, as.character) %>% 
  mutate(date = as.Date(as.numeric(date), origin = "1970-01-01")) %>% 
  rename(carrosserie = Carrosserie,
         energie = Energie,
         etat_vehicule = Etat.du.véhicule,
         transmission = Transmission,
         controle_technique = Contrôle.technique,
         couleur_interieur = Couleur.intérieur,
         type_peinture_carrosserie = Type.de.peinture.carrosserie,
         marque = Marque
         ) %>% 
  left_join(relevant_mapping_villes,  by= c("postal_code_city" = "codes_postaux_commune")) %>% 
  distinct() %>% 
  select(-Kilométrage,
         -Puissance.fiscale,
         -Puissance.réelle,
         -Garantie.mécanique,
         -Option.equipement.Sécurité,
         -Option.Equipement.Confort.intérieur,
         -Option.equipement.extérieurs,
         -Nb.de.portes,
         -Nombre.de.places,
         -Consommation.mixte,
         -Emissions.de.CO2,
         -Prix,
         -Autres.informations,
         -Année,
         -address_particulier,
         -address_pro,
         -city_particulier,
         -city_pro,
         -codes_postaux,
         -all_address)


new_data <- new_data %>% mutate(latitude = case_when(all_city == "Paris" ~ 48.8534,
                                                     all_city == "Marseille" ~ 43.3,
                                                     all_city == "Lyon" ~ 45.75,
                                                     all_city == "CREUTZWALD" ~ 49.2,
                                                     all_city == "Nimes" ~ 43.8333,
                                                     TRUE ~ latitude),
                                 longitude = case_when(all_city == "Paris" ~ 2.3488,
                                                       all_city == "Marseille" ~ 5.4,
                                                       all_city == "Lyon" ~ 4.85,
                                                       all_city == "CREUTZWALD" ~ 6.6833,
                                                       all_city == "Nimes" ~ 4.35,
                                                       TRUE ~ longitude))

subset <- new_data %>% 
  filter(str_detect(postal_code_city,"france")) %>%
  

new_data %>% filter(is.na(latitude)) %>% distinct(postal_code_city)

# NA dans city_particulier
```


#### Writing the final csv

```{r}
#write_csv(new_data, path = "datasets/third_dataset_full.csv")
```



